prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis.

### 2022-05-31 inst/MyArticle/paper.Rmd
Add FAIR
b-fabric and FAIR text cosmetics

To ease the usage barriers of the R package to users not being familiar with statistics and R programming, we integrated some workflows into our Local Laboratory Information Management System (LIMS) [b-fabric](https://fgcz-bfabric.uzh.ch/) @bfabric.
This integration enables our users to select the input and basic settings in a graphical user interface. Then, as an output, the user receives a report including input files, the R markdown file, and R scripts necessary to replicate the analysis using their in-house R installation. In this way, we also support the reproducible science efforts of the community.

>>>>

To ease the usage barriers of the R package to users not being familiar with statistics and R programming, we integrated some workflows into our data management platform [b-fabric](https://fgcz-bfabric.uzh.ch/) @bfabric.
This integration enables our users to select the input and basic settings in a graphical user interface. Then, as an output, the user receives a report including input files, the R markdown file, and R scripts necessary to replicate the analysis using their in-house R installation. In this way,  [b-fabric](https://fgcz-bfabric.uzh.ch/) helps scientists meet requirements from funding agencies, journals, and academic institutions to publish data according to the FAIR (Findable, Accessible, Interoperable and Reusable) [@FAIR] data principles.
